---
title: On the Surgical Removal of Cardassian Cranial Implants
subtitle: A case study of a Cardassian patient
short-title: Cranial Implants
published: "Under review at *Starfleet Medical Journal*"
code-repo: "Access the code, data, and analysis at <https://git.starfleet.ufp/bashir/cranial-implants>"
author:
  - name: Julian Bashir
    email: jbashir@starfleet.ufp
    orcid: 0000-0002-3948-3914
    affiliations: 
      - id: ds9
        name: Starbase Deep Space Nine
    attributes:
      corresponding: true
  - name: Elim Garak
    email: tailor.spy@obsidianorder.card.gov
    affiliations:
      - ref: ds9
      - id: terok
        name: Terok Nor
abstract: |
  Space: the final frontier. These are the voyages of the starship *Enterprise* Its continuing mission: to explore strange new worlds. To seek out new life and new civilizations. To boldly go where no one has gone before!
thanks: |
  Placeholder text generated at <https://vlad-saling.github.io/star-trek-ipsum/>.
keywords:
  - surgery
  - espionage
  - brains
date: August 24, 2022
epigraph:
  - text: War is good for business. 
    source: Ferengi Rule of Aquisition 34
  - text: Peace is good for business. 
    source: Ferengi Rule of Aquisition 35
bibliography: references.bib
format:
  hikmah-pdf: default
---

We're acquainted with the wormhole phenomenon, but this... Is a remarkable piece of bio-electronic engineering by which I see much of the EM spectrum ranging from heat and infrared through radio waves, et cetera, and forgive me if I've said and listened to this a thousand times [@Lovelace:1842]. This planet's interior heat provides an abundance of geothermal energy. We need to neutralize the homing signal.

# Main section

It indicates a synchronic distortion in the areas emanating triolic waves. The cerebellum, the cerebral cortex, the brain stem,  the entire nervous system has been depleted of electrochemical energy [@Turing:1936]. 

```{r}
n_lights <- 2 + 2
n_lights
```

Any device like that would produce high levels of triolic waves. These walls have undergone some kind of selective molecular polarization. I haven't determined if our phaser energy can generate a stable field. We could alter the photons with phase discriminators.

## Subsection

Communication is not possible [@Keynes:1937]. The shuttle has no power (see @fig-n-lights). 

Using the gravitational pull of a star to slingshot back in time? We are going to Starbase Montgomery for Engineering consultations prompted by minor read-out anomalies. Probes have recorded unusual levels of geological activity in all five planetary systems. 

Assemble a team. Look at records of the Drema quadrant. Would these scans detect artificial transmissions as well as natural signals?

```{r plot-n-lights}
#| echo: false
#| label: fig-n-lights
#| fig-cap: There are four lights
#| fig-width: 5
#| fig-height: 1
#| fig-align: "center"
par(mar = c(0, 0, 0, 0))
plot(x = seq(1:n_lights), y = rep(1, 4), col = "darkgoldenrod1", 
     pch = 8, cex = 4, axes = TRUE, ann = FALSE, xlab = FALSE, ylab = FALSE)
```
